### 2016-09-30 architecture.tex
SymPy never uses the phrase "terminal node"
Remove "so"

In SymPy every symbolic expression is an instance of the class
\texttt{Basic},\footnote{Some internal classes, such as those used in the
  polynomial submodule, do not follow this rule for efficiency reasons.} the
superclass of all SymPy types providing common methods to all SymPy
tree-elements, such as traversals. The children of a node in the tree are held
in the \texttt{args} attribute. A terminal or leaf node in the expression tree
has empty \texttt{args}.

For example, consider the expression $xy + 2$:
\begin{verbatim}
>>> x, y = symbols('x y')
>>> expr = x*y + 2
\end{verbatim}
By order of operations, the parent of the expression tree for \texttt{expr} is
an addition, so it is of type \texttt{Add}. The child nodes of \texttt{expr} are
\texttt{2} and \texttt{x*y}.
\begin{verbatim}
>>> type(expr)
<class 'sympy.core.add.Add'>
>>> expr.args
(2, x*y)
\end{verbatim}

>>>>

In SymPy every symbolic expression is an instance of the class
\texttt{Basic},\footnote{Some internal classes, such as those used in the
  polynomial submodule, do not follow this rule for efficiency reasons.} the
superclass of all SymPy types providing common methods to all SymPy
tree-elements, such as traversals. The children of a node in the tree are held
in the \texttt{args} attribute. A leaf node in the expression tree
has empty \texttt{args}.

For example, consider the expression $xy + 2$:
\begin{verbatim}
>>> x, y = symbols('x y')
>>> expr = x*y + 2
\end{verbatim}
By order of operations, the parent of the expression tree for \texttt{expr} is
an addition. It is of type \texttt{Add}. The child nodes of \texttt{expr} are
\texttt{2} and \texttt{x*y}.
\begin{verbatim}
>>> type(expr)
<class 'sympy.core.add.Add'>
>>> expr.args
(2, x*y)
\end{verbatim}
